### 2017-01-10 doc/manuscript.Rmd
Changed HOMA-IR methods to HOMA2-%S

Insulin sensitivity and beta-cell function indices were computed using the OGTT 
glucose and insulin data. Insulin sensitivity was assessed using 1/HOMA-IR (1
divided by HOMA-IR) [@Matthews1985] and the Insulin Sensitivity Index (ISI)
[@Matsuda1999]. HOMA-IR largely reflects hepatic insulin resistance, while ISI
reflects whole-body insulin sensitivity [@AbdulGhani2007]. Beta-cell function
was assessed using the Insulinogenic Index [@Wareham1995] over HOMA-IR (IGI/IR)
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR
is a measure of the first phase of insulin secretion while ISSI-2 is analogous to
the disposition index (but using OGTT values). Each index has been validated
against gold standard measures [@Matthews1985; @Matsuda1999; @Retnakaran2009].
Specific formulas for each OGTT-derived measure can be found in the {{
Supplementary Material }}.

The primary outcome variables for this analysis were 1/HOMA-IR, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the participants at the 6-year visit (n = `r n_tag`).
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables. Correlations were also
computed for TAGFA against each other, followed by using hierarchical clustering
analysis to identify clusters within the correlation matrix of the TAGFA
composition.

>>>>

Insulin sensitivity and beta-cell function indices were computed using the OGTT 
glucose and insulin data. Insulin sensitivity was assessed using HOMA2-%S
[@Levy1998a] using the HOMA2 Calculator and the Insulin Sensitivity Index (ISI)
[@Matsuda1999]. HOMA largely reflects hepatic insulin resistance, while ISI
reflects whole-body insulin sensitivity [@AbdulGhani2007]. Beta-cell function
was assessed using the Insulinogenic Index [@Wareham1995] over HOMA-IR [@Matthews1985] (IGI/IR)
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR
is a measure of the first phase of insulin secretion while ISSI-2 is analogous to
the disposition index (but using OGTT values). Each index has been validated
against gold standard measures [@Matthews1985; @Hermans1999a; @Matsuda1999; @Retnakaran2009].
Specific formulas for each OGTT-derived measure can be found in the {{
Supplementary Material }}.

The primary outcome variables for this analysis were HOMA2-%S, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the participants at the 6-year visit (n = `r n_tag`).
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables. Correlations were also
computed for TAGFA against each other, followed by using hierarchical clustering
analysis to identify clusters within the correlation matrix of the TAGFA
composition.
